### 2020-05-25 writeup/experiments.tex

\paragraph{A metric to determine when MTL performs better STL.}
\begin{table}
\begin{center}
  \begin{tabular}{c c c c c}
  \toprule
    \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
    & Precision &  Recall & Precision &  Recall \\
    \cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
    0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
    0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
    0.3 & 1.000 & 0.004 &     - &     - \\
  \bottomrule
  \end{tabular}
\end{center}
\caption{Ablation study on when should use MTL via different source/target task accuracy. Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.}
\label{tab:mtl_better_than_stl}
\end{table}

\paragraph{When should we align task covariances in MTL.}
\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
	\caption{Covariate shift experiment.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mlp.pdf}
	\caption{Covariate shift experiment.}
\end{figure}

>>>>

\subsection{Experimental Setup}

{\bf Datasets and models.} We describe the datasets and models we use in the experiments.

{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.

{For each task, the goal is to categorize sentiment opinions expressed in the text.
We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}\footnote{We also tested with multi-layer perceptron and CNN. The results are similar (cf. Appendix \ref{label:real_result_details}).}.
}
%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

{\it ChestX-ray14:} This dataset contains 112,120 frontal-view X-ray images and each image has up to 14 diseases.
This is a 14-task multi-label image classification problem.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.

For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.

\subsection{Results and Analysis}

\textbf{A metric to determine positive versus negative transfer.}
We propose a simple metric to determine whether multi-task learning performs better than single-task learning.
The metric is as follows.
First, we train 2 single-task models on 2 separate tasks.
We take the prediction accuracy of the two tasks.
Let $\tau$ be a fixed threshold.
If the accuracy of the source task is higher than the accuracy of the target task by $\tau$, then we predict positive transfer.
On the other hand, if the accuracy of the source task is lower than the accuracy of the target task by $\tau$, then we predict negative transfer.

Table \ref{tab:mtl_better_than_stl} shows the results on a sentiment analysis and an image classification task.

\begin{table}
\begin{center}
  \begin{tabular}{c c c c c}
  \toprule
    \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
    & Precision &  Recall & Precision &  Recall \\
    \cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
    0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
    0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
    0.3 & 1.000 & 0.004 &     - &     - \\
  \bottomrule
  \end{tabular}
\end{center}
\caption{Ablation study on when should use MTL via different source/target task accuracy. Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.}
\label{tab:mtl_better_than_stl}
\end{table}

\textbf{Measuring data efficiency ratio.}
We measure the data efficiency ratio on text classification tasks.
We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.

\textbf{Data size affects covariance alignment.}
We validate that the performance of aligning task covariances depends on the size of source task data.
Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.

In Figure \ref{fig_covariate}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_norm_lstm.pdf}
		\caption{LSTM (averaged)}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_norm_mlp.pdf}
		\caption{MLP (averaged)}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{LSTM for one pair}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size.}
	\label{fig_covariate}
\end{figure}

%\begin{figure}
%	\centering
%	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mlp.pdf}
%	\caption{Covariate shift experiment.}
%\end{figure}
